Network packet generation for Artificial Intelligence\\

### 2020-02-27 paper1/paper1.tex
Added summary and conclusion

\begin{IEEEkeywords}
artificial intelligence, neuronal networks, computer networks, network security, packet generation
\end{IEEEkeywords}

\section{Introduction}
Generating network traffic that can be used to train a neuronal network brings some challenges: there are many different attack types that need to be considered, a vast variety of attack tools to generate malicious traffic are available in the Internet each with their own advantages and disadvantages and generating realistic network traffic that does not get mislabeled by intrusion detection systems just to name a few.

@@

\begin{figure}[htbp]  
\centerline{\includegraphics[scale=.90]{computer-network-attacks.jpg}}
\caption{Ratio of computer and network attacks \cite{b2}}
\end{figure}

@@

\smallskip Physical attacks: this type of attack aims to cause physical damage to target systems (i.e. computers or networks). This includes, for example, deliberately cutting network cables or destroying computers \cite{b2}.
Password attacks: here an attempt is made to find out a specific password in order to gain control over a PC, for example. This can be done in three different ways: trying out all possible password combinations (brute force), trying out a part of all possible password combinations (e.g. testing simple passwords) and determining deficiencies in password storage / encryption \cite{b2,b5}.

@@

\begin{figure}[htbp]  
\centerline{\includegraphics[scale=.55]{network-tools.jpg}}
\caption{Taxonomy of network security tools \cite{b1}}
\end{figure}

@@

\section{Summary and conclusion}

>>>>

\begin{IEEEkeywords}
artificial intelligence, neural networks, computer networks, network security, packet generation
\end{IEEEkeywords}

\section{Introduction}
Generating network traffic that can be used to train a neural network brings some challenges: there are many different attack types that need to be considered, a vast variety of attack tools to generate malicious traffic are available in the Internet each with their own advantages and disadvantages and generating realistic network traffic that does not get mislabeled by intrusion detection systems just to name a few.

@@

\begin{figure}[htbp]  
\centerline{\includegraphics{computer-network-attacks.jpg}}
\caption{Ratio of computer and network attacks \cite{b2}}
\end{figure}

@@

\smallskip Physical attacks: this type of attack aims to cause physical damage to target systems (i.e. computers or networks). This includes, for example, deliberately cutting network cables or destroying computers \cite{b2}.

\smallskip Password attacks: here an attempt is made to find out a specific password in order to gain control over a PC, for example. This can be done in three different ways: trying out all possible password combinations (brute force), trying out a part of all possible password combinations (e.g. testing simple passwords) and determining deficiencies in password storage / encryption \cite{b2,b5}.

@@

\begin{figure}[htbp]  
\centerline{\includegraphics[scale=.65]{network-tools.jpg}}
\caption{Taxonomy of network security tools \cite{b1}}
\end{figure}

@@

\section{Summary and conclusion}
Various aspects must be taken into account for the generation of realistic network traffic for the production of a dataset, which is subsequently used for supervised machine learning. In the course of this paper, cyber-attacks were explained in principle, various tools for carrying out the attacks were shown, and how realistic network traffic based on benign and malicious data packets can be generated. The topics covered are summarized at this point in order to emphasize the most important content again.

Cyber -attacks generally try to exploit various vulnerabilities and carry out malicious actions. In order to provide an overview of the multitude of different attack methods, there are various approaches in the literature to classify the attacks into a few groups. The focus of this work is the classification model found in  \cite{b5}, which aims to enable a holistic view of attacks. Basically, nine different attack classes are described, including network attacks, denial of service attacks, information gathering attacks and various types of malware-based attacks. Subsequently, various attack targets (software, hardware and network), as well as vulnerabilities (in design, implementation, configuration) are explained in more detail.
Tools for carrying out-cyber attacks are basically divided into two different groups, namely information gathering tools and attack launching tools. The former tries to find out various information about the system to be attacked (open ports, operating system used, etc.). Sniffing and scanning tools can be used for this. Attack launching tools for performing denial of service attacks and for packet forging were identified. Furthermore, it is also possible to proceed on the basis of legitimate requests on the application layer. The creation of realistic network traffic based on benign and malicious data packets is a complex undertaking. By using tools, various strategies exist to generate harmless traffic, for example by using software robots.

\section{Further research}
Future work on this topic could try to look at attack methods on a more detailed level in order to provide specific information. Furthermore, it makes sense to identify additional tools for carrying out cyber-attacks. There is also room for further research in the search for other ways of generating realistic network traffic including benign and malicious behavior.
